Humann2 bar plot by myself

### 2019-10-17 scripts/08_barplot_species_pathway.Rmd
finally able to produce the damn bar pltos

```{r}
# ok so the correct format should be header at the first row, and phenotype and then the abundance values 
# pheno table 
read_csv('../data/cleaned_pheno/current_pheno.csv') %>% 
  filter(Sampleid %in% valid_s$X1) %>% 
  select(-Censor_YN, -Censor_reason) %>% 
  # USE THE Toxicity PHENO FIRST
  select(Sampleid, Toxicity) %>% 
  t() %>% 
  write.table('../data/horizontal_pheno/tox_wi_sample_header.txt', quote = F, row.names = T, col.names = F, sep = '\t')

@@

```{bash}
# the actual cmd to plot 
humann2_barplot  \
  --input ../data/humann2_res/humann2_final_out/humann2_pathabundance_relab_stratified_reordered_with_tox.tsv \
  --focal-feature PWY-4242 \
  --sort similarity sum metadata \
  --focal-metadatum Toxicity --last-metadatum Toxicity \
  --scaling pseudolog \
  --dimensions 10 5 \
  -o ../figs/PWY-4242_pw.png
```

>>>>

```{r}
# ok so the correct format should be header at the first row, and phenotype and then the abundance values 
valid_s <- read_table('../data/input_for_cluster_sampleid/valid_sample_names.txt', col_names = F)
# pheno table 
read_csv('../data/cleaned_pheno/current_pheno.csv') %>% 
  filter(Sampleid %in% valid_s$X1) %>% 
  select(-Censor_YN, -Censor_reason) %>% 
  # USE THE Toxicity PHENO FIRST
  select(Sampleid, Toxicity) %>% 
  t() %>% 
  write.table('../data/horizontal_pheno/tox_wi_sample_header.txt', quote = F, row.names = T, col.names = F, sep = '\t')

@@

```{bash}
# the actual cmd to plot 
humann2_barplot  \
  --input ../data/humann2_res/humann2_final_out/humann2_pathabundance_relab_stratified_reordered_with_tox.tsv \
  --focal-feature PWY-4242 \
  --sort similarity sum metadata \
  --focal-metadatum Toxicity --last-metadatum Toxicity \
  --scaling pseudolog \
  --dimensions 10 5 \
  -o ../figs/barplot_humann2/PWY-4242_pw.png
```

### now make the cmd with str_glue

```{r}
# load the sig pathway table with pwid
cmd_barplot <- read_csv('../data/unique_sig_pathway_with_clean_pwid.csv') %>% 
  select(pwid) %>% 
  mutate(barcmd = str_glue('humann2_barplot  --input ../data/humann2_res/humann2_final_out/humann2_pathabundance_relab_stratified_reordered_with_tox.tsv --focal-feature {pwid} --sort similarity sum metadata --focal-metadatum Toxicity --last-metadatum Toxicity --scaling pseudolog --dimensions 10 5 -o ../figs/barplot_humann2/{pwid}_pw.png')) %>% 
  select(barcmd)

cmd_barplot %>% 
  write.table('humann2_bar_cmd.sh', quote = F, col.names = F, row.names = F )
```

```{bash}
bash humann2_bar_cmd.sh
```

### 2019-10-17 scripts/09_barplot_myself.Rmd
finally able to produce the damn bar pltos

```{r}
# load the table that has the unique sig PATHWAYIDs
sigpw <- read_csv('../data/unique_sig_PATHWAYID.csv') %>% 
  # grab the pw id which is gonna be able to match the rownames in the stratified table
  mutate(pwid = str_extract(PATHWAYID, '^.+_PWY|^PWY_\\d{3,4}'))  %>% 
  mutate(pwid = str_replace_all(pwid, '_', '-'))

# find how many species total it has in all of the lefse sig PATHWAYIDs
siglefse <- stratified %>% 
  filter(str_detect(PATHWAYID,  paste0(sigpw$pwid, collapse = '|'))) %>% 
  separate(PATHWAYID, into = c('pwid','taxa'), sep = '\\|')

@@

```

>>>>

```{r}
# load the table that has the unique sig PATHWAYIDs
sigpw <- read_csv('../data/unique_sig_pathway.csv') %>% 
  # grab the pw id which is gonna be able to match the rownames in the stratified table
  mutate(pwid = str_extract(pathway, '^.+_PWY|^PWY_\\d{3,4}'))  %>% 
  mutate(pwid = str_replace_all(pwid, '_', '-'))

# find how many species total it has in all of the lefse sig PATHWAYIDs
siglefse <- stratified %>% 
  filter(str_detect(pathway,  paste0(sigpw$pwid, collapse = '|'))) %>% 
  separate(pathway, into = c('pwid','taxa'), sep = '\\|')

@@

# aoutput the reformatted sigpw table
sigpw %>% 
  write_csv('../data/unique_sig_pathway_with_clean_pwid.csv')
```
